```{r}
```{r setup, message = FALSE, warning = FALSE, echo = FALSE, include = FALSE}

knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(RODBC)
```

```{r get data from sql}

dsn <- "VhaCdwDwhSql33.vha.med.va.gov"
con <- odbcConnect(dsn, uid = "",  pwd = "")
query <- c("
SELECT
  PatientSSN,
  PatientLastName,
  PatientFirstName,
  ArrivalDate,
  VitalsDate,
  VitalsTime,
  VitalType,
  Systolic,
  Result

FROM
  (
  SELECT DISTINCT
    SPat.PatientSSN AS PatientSSN,
    SPat.PatientLastName AS PatientLastName,
    SPat.PatientFirstName AS PatientFirstName,
    CAST(EDIS.PatientArrivalDateTime AS date) AS ArrivalDate,
    CAST(Vitals.VitalSignEnteredDateTime AS date) AS VitalsDate,
    CAST(Vitals.VitalSignEnteredDateTime AS time) AS VitalsTime,
    VitalType.VitalType AS VitalType,
    Vitals.Systolic AS Systolic,
    Vitals.VitalResult AS Result
  
  FROM
    LSV.SPatient.SPatient AS SPat
    INNER JOIN LSV.EDIS.EDISlog AS EDIS
      ON SPat.PatientSID = EDIS.PatientSID
  	  AND SPat.Sta3n = EDIS.Sta3n
    INNER JOIN LSV.Vital.VitalSign AS Vitals
      ON EDIS.PatientSID = Vitals.PatientSID
  	  AND EDIS.Sta3n = Vitals.Sta3n
	  AND EDIS.LocationSID = Vitals.LocationSID
    INNER JOIN LSV.Dim.VitalType AS VitalType
      ON Vitals.VitalTypeSID = VitalType.VitalTypeSID
  	  AND Vitals.Sta3n = VitalType.Sta3n
  
  WHERE
    SPat.PatientSSN IN ('')
    AND SPat.Sta3n = '612'
    AND EDIS.PatientArrivalDateTime >=  DATEADD(day, -30, GETDATE())
    AND Vitals.VitalSignEnteredDateTime BETWEEN EDIS.PatientArrivalDateTime AND DATEADD(hour, +1, EDIS.PatientArrivalDateTime)
    AND VitalType.VitalType IN ('PULSE', 'TEMPERATURE', 'RESPIRATION', 'BLOOD PRESSURE')

  GROUP BY
      SPat.PatientSSN,SPat.PatientLastName,SPat.PatientFirstName,EDIS.PatientArrivalDateTime,Vitals.VitalSignEnteredDateTime,Vitals.VitalSignEnteredDateTime,VitalType.VitalType,Vitals.Systolic,Vitals.VitalResult
  ) AS InnerQ

WHERE
  ArrivalDate = VitalsDate
  
GROUP BY
  PatientSSN, PatientLastName, PatientFirstName, ArrivalDate, VitalsDate, VitalsTime, VitalType, Systolic, Result
")
backup_dat <- sqlQuery(con, query)
odbcCloseAll()
rm('con', 'dsn', 'query')
```

```{r data manipulation}

dat <- backup_dat

dat$value <- as.character(dat$Result) %>% sapply( function(x) { if (!grepl("/",as.character(x))) x else strsplit(x,'/')[[1]][1]}) %>% as.numeric()

dat <- select(dat, -Systolic, -Result)
dat <- backup_dat 
dat <- as_tibble(dat)
dat$VitalsTime[1] <- "09:31:22.0000000"
dat <- dat %>% spread(dat, key = VitalType, value = value, convert = TRUE)

